---
title: "Homework 8 Group"
author: "Elijah Lipkin, Krishna Goel, Toby Han"
date: "10/25/2018"
output: pdf_document
---

```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(knitr)
library(RSQLite)

setwd("C://Users//kgoel//Desktop//Y3 Sem1//Stat 405//Overall Project")

dcon.urban <- dbConnect(SQLite(), dbname = "urbanlite.sqlite")
dcon.yt <- dbConnect(SQLite(), dbname = "youtubelite.sqlite")

dbSendQuery(conn = dcon.yt, "DROP TABLE subset_yt")
dbSendQuery(conn = dcon.urban, "DROP TABLE subset_urban")
```

```{r Exercise 5.1, echo=FALSE}
dbListTables(dcon.urban)
dbListTables(dcon.yt)

dbListFields(dcon.urban, "per_word")
dbListFields(dcon.yt, "youtube_entries")

res.u <- dbSendQuery(conn = dcon.urban, "
CREATE TABLE subset_urban AS
SELECT word,
thumbs_up
FROM per_word
WHERE thumbs_up < 6500 AND
thumbs_up > 4500
ORDER BY thumbs_up")
dbClearResult(res.u)
```
Here, we select words we would qualify as moderately popular based on their number of thumbs up received on Urban Dictionary. 

```{r Exercise 5.2, echo=FALSE}
res.yt <- dbSendQuery(conn = dcon.yt, "
CREATE TABLE subset_yt AS
SELECT title, 
tags,
views,
likes
FROM youtube_entries
WHERE views > '1000000' AND
likes < '100000'
ORDER BY likes")
subset.yt <- dbFetch(res.yt, -1)
dbClearResult(res.yt)
```
And here, we pick out videos we'd consider to be moderately popular on YouTube. The goal here is to compare the words in the descriptions/tags of the videos with the actual words from Urban Dictionary to see how they relate, if at all.

```{r Exercise 5.3, echo=FALSE}
res.u <- dbSendQuery(conn = dcon.urban, "
SELECT *
FROM subset_urban;
")
mydf.u <- dbFetch(res.u, -1)
dbClearResult(res.u)
head(mydf.u)
```
This is the creation of a data frame from the Urban Dictionary data we just extracted. It can now be used to compare and subset within R. 

```{r Exercise 5.4, echo = FALSE}
res.yt <- dbSendQuery(conn = dcon.yt, "
SELECT *
FROM subset_yt;
")
mydf.yt <- dbFetch(res.yt, -1)
dbClearResult(res.yt)

head(mydf.yt)
```
This is the creation of a data frame from the YouTube data we just extracted. It can now be used to compare and subset within R. 


