---
title: "Group Project Part 2"
author: "Krishna Goel, Toby Han, Elijah Lipkin"
date: "October 3, 2018"
output: pdf_document
---

### Setup:

```{r, echo = TRUE, warning = FALSE, message = FALSE}
setwd("C://Users//kgoel//Desktop//Y3 Sem1//Stat 405//Overall Project")

library(dplyr)
library(stringi)
library(ggplot2)

word_frequencies <- read.csv("data.csv")
fixed_words <- mutate(word_frequencies, word = stri_sub(word, 3, -4))
head(fixed_words)
```

Mutating because the strings we got were misformatted and the API had kicked us out for too many requests. We have a bigger data set downloaded, but we just wanted to demonstrate we could apply dsplyr to the dataset for now. The full csv was too big for R to open. (This data set is a approxiamtly 1000 words startin in "a" that were processed in python to get the total upvotes for each word as that doesn't come by default from the API)

### Processing intermediate data in dplyr


#### Part 1

Arranged data to see range of upvotes

```{r, echo = TRUE, warning = FALSE}
arranged <- arrange(fixed_words, desc(total_upvotes))
head(arranged)
```

#### Part 2

Got various subsets of the data based on upvote range, some metrics to see what the data looks like an how many rows it contains

```{r, echo = TRUE, warning=FALSE}
filtered_top <- filter(arranged, total_upvotes > 10000)
head(filtered_top)
nrow(filtered_top)

filtered_mid <- filter(arranged, total_upvotes > 6000, total_upvotes < 10000)
head(filtered_mid)
nrow(filtered_mid)

filtered_mid_low <- filter(arranged, total_upvotes > 2000, total_upvotes < 3000)
head(filtered_mid_low)
nrow(filtered_mid_low)

filtered_low <- filter(arranged, total_upvotes > 500, total_upvotes < 1000)
head(filtered_low)
nrow(filtered_low)
```

### Plotting the data to get an idea of what types of words appear

```{r, echo = TRUE}
ggplot(data = filtered_top) +
  aes(factor(word), total_upvotes, fill = "#2e7f1e") +
  geom_col(position = "identity") +
  labs(x = "Word", 
       y = "Number of Up-votes",
       title = "Top Words") +
  theme(axis.text.x = element_text(angle = 40, hjust = 1)) +
  theme(legend.position="none")

ggplot(data = filtered_mid) +
  aes(factor(word), total_upvotes, fill = "#1a2e89") +
  geom_col(position = "identity") +
  labs(x = "Word", 
       y = "Number of Up-votes",
       title = "Mid Words") +
  theme(axis.text.x = element_text(angle = 40, hjust = 1)) +
  theme(legend.position="none")

ggplot(data = filtered_mid_low) +
  aes(factor(word), total_upvotes, fill = "#1a2e89") +
  geom_col(position = "identity") +
  labs(x = "Word", 
       y = "Number of Up-votes",
       title = "Mid to Low Words") +
  theme(axis.text.x = element_text(angle = 40, hjust = 1)) +
  theme(legend.position="none")

ggplot(data = filtered_low) +
  aes(factor(word), total_upvotes, fill = "#1a2e89") +
  geom_col(position = "identity") +
  labs(x = "Word", 
       y = "Number of Up-votes",
       title = "Low Words") +
  theme(axis.text.x = element_text(angle = 40, hjust = 1)) +
  theme(legend.position="none")
```

